### 2020-06-30 Report/aws_325ghz_study.tex
small changes after merge

The basic shape of the Jacobian is similar for all 183 and 325\,GHz channels,
but the peak altitude varies. Again the edge 183\,GHz channels brackets the
325\,GHz ICI ones, as for transmissivity. These Jacobians are negative, meaning
that a change towards higher humidity results in decreased brightness
temperatures. The 229\,GHz Jacobian is positive close to the surface, as this
channel has sensitivity all the way down to the surface and more water vapour
just above a reflecting surface results in higher brightness temperatures. The
switch from negative to positive Jacobian depends on atmospheric scenario and
surface reflectivity. For dry conditions also the outer 183 and 325\,GHz
channels can have a positive part, as long as the reflectivity is not close to
0.

@@

\begin{figure}[!tb]
	\centering
	\includegraphics[height=100mm]{PDF_corrected_AWS-34_AWS-42_allfits}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction, corrected using a linear,
      quadratic and cubic model. The distribution of noise alone is also shown
      as reference. The measurements have been corrected using brightness
      temperatures from AWS-42. The clear/cloudy classification is made with $dtb_{cs} = 1\sigma$ and also cases with $Tb2 - Tb1 > -15$\,K are rejected.}
	\label{fig:correction:c34-42:fit}
\end{figure}
%
\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness  & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
		noise                     &   0.00 &  0.63 &               0.00 &                - \\
		uncorrected-all           &  -0.75 &  4.62 &             -11.78 &                - \\
		corrected-linear model    &  -0.03 &  0.75 &               0.48 &                2.84 \\
		corrected-quadratic model &  -0.06 &  0.71 &              -0.34 &                2.84 \\
		corrected-cubic model     &  -0.05 &  0.72 &              -0.23 &                2.84 \\
		\hline
	\end{tabular}
	\caption{Bias, standard deviation (std), and measure of skewness of error
      distributions shown in Figure~\ref{fig:correction:c34-42:fit}. The
      fraction rejected describes the percentage of cases which are removed.
      Results from three different fit models are shown: linear, quadratic and
      cubic.}
	\label{tab:correction:stats:34:42:allfits}
\end{table}
%
\begin{figure}[!tb]
  \centering \includegraphics[height=100mm]{PDF_corrected_AWS-34_AWS-42_thinned}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction. The measurements have been
      corrected using a cubic model. The different datasets are: noise
      (simulation dataset), uncorrected (thinned measurements), filtered $1\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 1$\sigma$ are rejected), corrected $1\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 1$\sigma$ are corrected), corrected
      $2\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 2$\sigma$ are corrected), Sreerekha et al (cloudy cases are filtered according to \citet{rekha2012potential}).}
	\label{fig:correction:c34-42:thinned}
\end{figure}
%
\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness  & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	noise             		&   0.00 &  0.63 &              -0.01 &                - \\
	uncorrected     		&  -1.27 &  6.05 &              -8.97 &                - \\
	filtered($1\sigma$)  	&  -0.13 &  0.68 &              -0.25 &               17.54 \\
	corrected($1\sigma$) 	&  -0.06 &  0.76 &              -0.46 &                4.99 \\
	corrected($2\sigma$) 	&  -0.11 &  0.75 &              -0.69 &                4.99 \\
	sreerekha et al         &  -0.16 &  0.71 &              -0.46 &               46.37 \\			
		\hline
\end{tabular}
\caption{Bias, standard deviation (std), and measure of skewness of the error
  distributions of datasets shown in
  Figure~\ref{fig:correction:c34-42:thinned}.}
\label{tab:correction:stats:34:42:thinned}
\end{table}

@@

Some further channel options were included on the DoF analysis. Staying inside
0.8\,-\,8.0\,GHz in terms of IF, the option three-c was found to have the
highest overall DoF, but the differences to three-b and four are relatively
small. However, it could be challenging to implement any of the three channel
options. The option three-a risks to be affected by interference of the downlink
and in the options three-b and c there is a high ratio between bandwidth and centre IF of AWS-42. The latter aspect also makes it hard to extend options three-b and c, if it would turn out that the IF range can be extended. A brief analysis showed that a broader IF range gives some increase in DoF, that potentially could improve the merit of the four channel option.

>>>>

The basic shape of the Jacobian is similar for all 183 and 325\,GHz channels,
but the peak altitude varies. Again the edge 183\,GHz channels bracket the
325\,GHz ICI ones, as for transmissivity. These Jacobians are negative, meaning
that a change towards higher humidity results in decreased brightness
temperatures. The 229\,GHz Jacobian is positive close to the surface, as this
channel has sensitivity all the way down to the surface and more water vapour
just above a reflecting surface results in higher brightness temperatures. The
switch from negative to positive Jacobian depends on atmospheric scenario and
surface reflectivity. For dry conditions also the outer 183 and 325\,GHz
channels can have a positive part, as long as the reflectivity is not close to
0.

@@

\begin{figure}[!tb]
	\centering
	\includegraphics[height=100mm]{PDF_corrected_AWS-34_AWS-42_allfits}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction, corrected using a linear,
      quadratic and cubic model. The distribution of noise alone is also shown
      as reference. The measurements have been corrected using brightness
      temperatures from AWS-42. The clear/cloudy classification is made with $dtb_{cs} = 1\sigma$ and also cases with $Tb2 - Tb1 > -15$\,K are rejected.}
	\label{fig:correction:c34-42:fit}
\end{figure}
%
\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness  & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
		noise                     &   0.00 &  0.63 &               0.00 &                - \\
		uncorrected-all           &  -0.75 &  4.62 &             -11.78 &                - \\
		corrected-linear model    &  -0.03 &  0.75 &               0.48 &                2.84 \\
		corrected-quadratic model &  -0.06 &  0.71 &              -0.34 &                2.84 \\
		corrected-cubic model     &  -0.05 &  0.72 &              -0.23 &                2.84 \\
		\hline
	\end{tabular}
	\caption{Bias, standard deviation (std), and measure of skewness of error
      distributions shown in Figure~\ref{fig:correction:c34-42:fit}. The
      fraction rejected describes the percentage of cases which are removed.
      Results from three different fit models are shown: linear, quadratic and
      cubic.}
	\label{tab:correction:stats:34:42:allfits}
\end{table}
%
\begin{figure}[!tb]
  \centering \includegraphics[height=100mm]{PDF_corrected_AWS-34_AWS-42_thinned}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction. The measurements have been
      corrected using a cubic model. The different datasets are: noise
      (simulation dataset), uncorrected (thinned measurements), filtered $1\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 1$\sigma$ are rejected), corrected $1\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 1$\sigma$ are corrected), corrected
      $2\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 2$\sigma$ are corrected), Sreerekha et al (cloudy cases are filtered according to \citet{rekha2012potential}).}
	\label{fig:correction:c34-42:thinned}
\end{figure}
%
\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness  & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	noise             		&   0.00 &  0.63 &              -0.01 &                - \\
	uncorrected     		&  -1.27 &  6.05 &              -8.97 &                - \\
	filtered($1\sigma$)  	&  -0.13 &  0.68 &              -0.25 &               17.54 \\
	corrected($1\sigma$) 	&  -0.06 &  0.76 &              -0.46 &                4.99 \\
	corrected($2\sigma$) 	&  -0.11 &  0.75 &              -0.69 &                4.99 \\
	sreerekha et al         &  -0.16 &  0.71 &              -0.46 &               46.37 \\			
		\hline
\end{tabular}
\caption{Bias, standard deviation (std), and measure of skewness of the error
  distributions of datasets (AWS-34) shown in
  Figure~\ref{fig:correction:c34-42:thinned}.}
\label{tab:correction:stats:34:42:thinned}
\end{table}

@@

Some further channel options were included on the DoF analysis. Staying inside
0.8\,-\,8.0\,GHz in terms of IF, the option three-c was found to have the
highest overall DoF, but the differences to three-b and four are relatively
small. However, it could be challenging to implement any of the three channel
options. The option three-a risks to be affected by interference of the downlink
and in the options three-b and c there is a high ratio between bandwidth and centre IF of AWS-42. The latter aspect also makes it hard to extend options three-b and c, if it would turn out that the IF range can be extended. A brief analysis showed that a broader IF range gives some increase in DoF, that potentiallyacould improve the merit of the four channel option.
